Predicting trends in the quality of state-of-the-art neural networks without access to training or testing data

### 2020-07-06 submission/abstract_file.tex
removed red and fixed some typos

In many practical applications, one works with deep neural network (DNN) models trained by someone else.
For such \emph{pretrained models}, one often does not have access to training data or test data.
Moreover, one may not know many details about the model, such as the specifics of the training data, the loss function, the hyperparameter values, etc.
Given one or many pretrained models, can one say anything about the expected performance or quality of the models?
Here, we provide a detailed empirical meta-analysis to address this question, evaluating quality metrics for pretrained DNN models at scale.
%%Our metrics are drawn from traditional statistical learning theory (e.g., norm-based capacity control metrics) as well as Heavy-Tailed Random Matrix Theory (HT-RMT), as used in the recently-developed Theory of Heavy-Tailed Self Regularization (e.g., fitted power law metrics used to characterize the degree of strong correlations in trained models).
%%The most promising are metrics drawn from traditional statistical learning theory (e.g., norm-based capacity control metrics) as well as metrics (e.g., fitted power law metrics used to characterize the degree of strong correlations in a system) derived from the recently-developed Theory of Heavy-Tailed Self Regularization (HT-SR).
%The most promising are norm-based metrics
% (such as those used to provide capacity control in traditional statistical learning theory) 
%and metrics based on fitting eigenvalue distributions to truncated power law (PL) distributions 
%(which derive from statistical mechanics, in particular the recently-developed Theory of Heavy-Tailed Self Regularization, and which characterize the strength of correlations in a DNN). 
%
Using the open-source \emph{WeightWatcher} tool to analyze DNN weight matrices, we analyze hundreds of publicly-available pretrained models, including older and current state-of-the-art models in computer vision (CV) and natural language processing (NLP).
We examine both familiar norm-based capacity control metrics (Frobenius and Spectral norms) as well as newer Power Law (PL) based metrics (including fitted PL exponents, $\alpha$, and the Weighted Alpha metric, $\hat{\alpha}$), from the recently-developed Theory of Heavy-Tailed Self Regularization (HT-SR).
We also introduce the $\alpha$-Shatten Norm metric.
We find that norm-based metrics correlate well with reported test accuracies for well-trained models across nearly all CV architecture series.
On the other hand, we find that norm-based metrics can not distinguish well-trained versus poorly-trained models---which, arguably is the point of needing quality metrics.  
%%%Indeed, they may give spurious results.
We also find that PL-based metrics do much better---qualitatively better at discriminating well-trained versus poorly-trained models, and quantitatively better at discriminating among a series of well-trained versus more-well-trained models.
PL-based metrics can also be used to characterize fine-scale properties of these models.
%%%, and we introduce the layer-wise \emph{Correlation Flow} as new quality assessment.
%%%We show how poorly-trained (and/or poorly fine-tuned) models may exhibit both \emph{Scale Collapse} and unusually large PL exponents, $\alpha\gg 6$, in particular for recent NLP models.
Our techniques, as implemented in the \emph{WeightWatcher} tool, can be used to identify when a pretrained DNN has problems that can not be detected simply by examining training/test accuracies.

>>>>

In many practical applications, one works with deep neural network (DNN) models trained by someone else.
For such \emph{pretrained models}, one often does not have access to training data or test data.
Moreover, one may not know many details about the model, such as the specifics of the training data, the loss function, the hyperparameter values, etc.
Given one or many pretrained models, can one say anything about the expected performance or quality of the models?
Here, we provide a detailed empirical meta-analysis to address this question, evaluating quality metrics for pretrained DNN models at scale.
%%Our metrics are drawn from traditional statistical learning theory (e.g., norm-based capacity control metrics) as well as Heavy-Tailed Random Matrix Theory (HT-RMT), as used in the recently-developed Theory of Heavy-Tailed Self Regularization (e.g., fitted power law metrics used to characterize the degree of strong correlations in trained models).
%%The most promising are metrics drawn from traditional statistical learning theory (e.g., norm-based capacity control metrics) as well as metrics (e.g., fitted power law metrics used to characterize the degree of strong correlations in a system) derived from the recently-developed Theory of Heavy-Tailed Self Regularization (HT-SR).
%The most promising are norm-based metrics
% (such as those used to provide capacity control in traditional statistical learning theory) 
%and metrics based on fitting eigenvalue distributions to truncated power law (PL) distributions 
%(which derive from statistical mechanics, in particular the recently-developed Theory of Heavy-Tailed Self Regularization, and which characterize the strength of correlations in a DNN). 
%
Using the open-source \emph{WeightWatcher} tool to analyze DNN weight matrices, we analyze hundreds of publicly-available pretrained models, including older and current state-of-the-art models in computer vision (CV) and natural language processing (NLP).
We examine both familiar norm-based capacity control metrics (Frobenius and Spectral norms) as well as newer Power Law (PL) based metrics (including fitted PL exponents, $\alpha$, and the Weighted Alpha metric, $\hat{\alpha}$), from the recently-developed Theory of Heavy-Tailed Self Regularization (HT-SR).
We also introduce the $\alpha$-Shatten Norm metric.
We find that norm-based metrics correlate well with reported test accuracies for well-trained models across nearly all CV architecture series.
On the other hand, we find that norm-based metrics can not distinguish well-trained versus poorly-trained models---which, arguably is the point of needing quality metrics.  
%%%Indeed, they may give spurious results.
We also find that PL-based metrics do much better---qualitatively better at discriminating well-trained versus poorly-trained models, and quantitatively better at discriminating among a series of well-trained models of increasing depth and accuracy.
%versus very-well-trained models.
PL-based metrics can also be used to characterize fine-scale properties of these models.
%%%, and we introduce the layer-wise \emph{Correlation Flow} as new quality assessment.
%%%We show how poorly-trained (and/or poorly fine-tuned) models may exhibit both \emph{Scale Collapse} and unusually large PL exponents, $\alpha\gg 6$, in particular for recent NLP models.
Our techniques, as implemented in the \emph{WeightWatcher} tool, can be used to identify when a pretrained DNN has problems that can not be detected simply by examining training/test accuracies.

### 2020-07-06 submission/background.tex
removed red and fixed some typos

There is also a large body of work on using norm-based metrics to bound generalization error~\cite{NTS15, BFT17_TR, LMBx18_TR}.
In this area, theoretical work aims to prove generalization bounds, and applied work uses these norms to construct regularizers to improve training.
While we do find that norms provide relatively good quality metrics, at least for distinguishing among well-trained versus more-well-trained models, we are not interested in proving generalization bounds or developing new regularizers.

>>>>

There is also a large body of work on using norm-based metrics to bound generalization error~\cite{NTS15, BFT17_TR, LMBx18_TR}.
In this area, theoretical work aims to prove generalization bounds, and applied work uses these norms to construct regularizers to improve training.
While we do find that norms provide relatively good quality metrics, at least for distinguishing among (moderately) well-trained versus 
very-well-trained models, of increasing depth and accuracy, 
we are not interested in proving generalization bounds or developing new regularizers.

### 2020-07-06 submission/cv_models.tex
removed red and fixed some typos

We have examined the performance of the four quality metrics (Log Frobenius norm, Log Spectral norm, Weighted Alpha, and Log $\alpha$-Norm) applied to each of the VGG, ResNet, ResNet-1K, and DenseNet series.
To start, Figure~\ref{fig:vgg-metrics} considers the VGG series (in particular, the pretrained models VGG11, VGG13, VGG16, and VGG19, with and without \nred{BatchNormalization, denoted} BN), and it plots the four quality metrics versus the reported test accuracies~\cite{pytorch},% 
\footnote{That is, these test accuracies have been previously reported and made publicly-available by others.  We take them as given, and we do not attempt to reproduce/verify them, since we do not permit ourselves any access to training/test data.}
as well as a basic linear regression line. 
All four metrics correlate quite well with the reported Top1 accuracies, with smaller norms and smaller values of $\hat{\alpha}$ implying better generalization (i.e., greater accuracy, lower error). 
While all four metrics perform well, notice that the Log $\alpha$-Norm metric ($\log\Vert\mathbf{W}\Vert_{\alpha}^{\alpha}$) performs best (with an RMSE of $0.42$, see Table~\ref{table:cv-models}); and the Weighted Alpha metric ($\hat\alpha =\alpha\log\lambda_{max} $), which is an approximation to the Log $\alpha$-Norm metric~\cite{MM20_unpub_work}, performs second best (with an RMSE of $0.48$, see Table~\ref{table:cv-models}).

>>>>

We have examined the performance of the four quality metrics (Log Frobenius norm, Log Spectral norm, Weighted Alpha, and Log $\alpha$-Norm) applied to each of the VGG, ResNet, ResNet-1K, and DenseNet series.
To start, Figure~\ref{fig:vgg-metrics} considers the VGG series (in particular, the pretrained models VGG11, VGG13, VGG16, and VGG19, with and without Batch Normalization, denoted BN), and it plots the four quality metrics versus the reported test accuracies~\cite{pytorch},% 
\footnote{That is, these test accuracies have been previously reported and made publicly-available by others.  We take them as given, and we do not attempt to reproduce/verify them, since we do not permit ourselves any access to training/test data.}
as well as a basic linear regression line. 
All four metrics correlate quite well with the reported Top1 accuracies, with smaller norms and smaller values of $\hat{\alpha}$ implying better generalization (i.e., greater accuracy, lower error). 
While all four metrics perform well, notice that the Log $\alpha$-Norm metric ($\log\Vert\mathbf{W}\Vert_{\alpha}^{\alpha}$) performs best (with an RMSE of $0.42$, see Table~\ref{table:cv-models}); and the Weighted Alpha metric ($\hat\alpha =\alpha\log\lambda_{max} $), which is an approximation to the Log $\alpha$-Norm metric~\cite{MM20_unpub_work}, performs second best (with an RMSE of $0.48$, see Table~\ref{table:cv-models}).

### 2020-07-06 submission/introduction.tex
removed red and fixed some typos

Na\"{\i}vely---but in our experience commonly, among ML practitioners and ML theorists---if one does not have access to training or testing data, then one can say absolutely nothing about the quality of a ML model.
This may be true in worst-case theory, but models are used in practice, and there is a need for a \emph{practical theory} to guide that practice.
Moreover, if ML is to become an industrial process, then that process will become siloed: some groups will gather data, other groups will develop models, and other groups will use those models.
Users of models can not be expected to know the precise details of how models were built, the specifics of data that were used to train the model, what was the loss function or hyperparameter values, how precisely the model was regularized,~etc.

@@

To answer this question, we perform a statistical meta-analysis, where we 
perform weight matrix analysis on %%%analyze 
hundreds of publicly-available pretrained state-of-the-art CV and NLP models. 
Here is a summary of our main results.
\begin{itemize}
\item
\textbf{Norm-based metrics and well-trained models.}
Norm-based metrics do a reasonably good job at predicting quality trends in well-trained CV/NLP models.
\item
\textbf{Norm-based metrics and poorly-trained models.}
Norm-based metrics may give spurious results when applied to poorly-trained models (e.g., models trained without enough data, etc.).
For example, they may exhibit what we call \emph{Scale Collapse} for these models. 
\item 
\textbf{PL-based metrics and model quality.}
PL-based metrics do much better at predicting quality trends in pretrained CV/NLP models.  
They are qualitatively better at discriminating well-trained versus poorly-trained models, and quantitatively better at discriminating among a series of well-trained versus more-well-trained models.
\item 
\textbf{PL-based metrics and model diagnostics.}
PL-based metrics can also be used to characterize fine-scale model properties (including what we call layer-wise \emph{Correlation Flow}) in well-trained and poorly-trained models, and they can be used to evaluate model enhancements (e.g., distillation, fine-tuning, etc.).
\end{itemize}

@@

All of our computations were performed with the publicly-available \emph{WeightWatcher} tool (version 0.2.7)~\cite{weightwatcher_package}.
To be fully reproducible, we only examine publicly-available, pretrained models, and we also provide all Jupyter and Google Colab notebooks used in an accompanying github repository~\cite{kdd20_sub_repo}.
See Appendix~\ref{sxn:appendix} for details on how to reproduce all results.

>>>>

Na\"{\i}vely---but in our experience commonly, among ML practitioners and ML theorists---if one does not have access to training or testing data, then one can say absolutely nothing about the quality of a ML model.
This may be true in worst-case theory, but models are used in practice, and there is a need for a \emph{practical theory} to guide that practice.
Moreover, if ML is to become an industrial process, then that process will become compartmentalized in order to scale: some groups will gather data, other groups will develop models, and other groups will use those models.
Users of models can not be expected to know the precise details of how models were built, the specifics of data that were used to train the model, what was the loss function or hyperparameter values, how precisely the model was regularized,~etc.

@@

To answer this question, we perform a statistical meta-analysis, where we 
perform weight matrix analysis on %%%analyze 
hundreds of publicly-available pretrained state-of-the-art CV and NLP models. 
Here is a summary of our main results.
\begin{itemize}
\item
\textbf{Norm-based metrics and well-trained models.}
Norm-based metrics do a reasonably good job at predicting quality trends in well-trained CV/NLP models.
\item
\textbf{Norm-based metrics and poorly-trained models.}
Norm-based metrics may give spurious results when applied to poorly-trained models (e.g., models trained without enough data, etc.).
For example, they may exhibit what we call \emph{Scale Collapse} for these models. 
\item 
\textbf{PL-based metrics and model quality.}
PL-based metrics do much better at predicting quality trends in pretrained CV/NLP models.  
They are qualitatively better at discriminating well-trained versus poorly-trained models, and quantitatively better at discriminating among a series of well-trained versus very-well-trained models.
\item 
\textbf{PL-based metrics and model diagnostics.}
PL-based metrics can also be used to characterize fine-scale model properties (including what we call layer-wise \emph{Correlation Flow}) in well-trained and poorly-trained models, and they can be used to evaluate model enhancements (e.g., distillation, fine-tuning, etc.).
\end{itemize}

@@

All of our computations were performed with the publicly-available \emph{WeightWatcher} tool (version 0.2.7)~\cite{weightwatcher_package}.
To be fully reproducible, we only examine publicly-available, pretrained models, and we also provide all Jupyter and Google Colab notebooks used in an accompanying github repository~\cite{kdd20_sub_repo}.
See Appendix~\ref{sxn:appendix} for details on how to reproduce all~results.

### 2020-07-06 submission/methods.tex
removed red and fixed some typos

Let us write the objective/optimization function (parameterized by $\mathbf{W}_{l}$s and $\mathbf{b}_{l}$s) for aE DNN with $L$ layers, activation functions $h_{l}(\cdot)$, and $N\times M$ weight matrices $\mathbf{W}_{l}$ and biases $\mathbf{b}_{l}$,~as \nred{the minimization of a general Loss Function $\mathcal{L}$ over  N training data instances and labels  $\{\mathbf{x}_{i},y_{i}\}\in\mathcal{D}$
For a typical supervised classification problem, one has
\begin{equation}
\underset{\mathbf{W}_{l},\mathbf{b}_{L}}{\text{argmin}}\;\sum_{i=1}^{N}\left(\mathcal{L}(E_{DNN}(\mathbf{x}_{i})-y_{i})\right)
\end{equation}
where the loss function $\mathcal{L}()$ can take on a myriad of forms\cite{Janocha2017}, and 
\begin{equation}
E_{DNN}=h_{L}(\mathbf{W}_{L}\times h_{L-1}(\mathbf{W}_{L-1}\times h_{L-2}(\cdots)+\mathbf{b}_{L-1})+\mathbf{b}_{L})
\label{eqn:dnn_energy}
\end{equation}
is what we call the Energy Landscape function.  Notice the $E_{DNN}$ does not explicitly depend on the data, but, rather,
maps data instances vectors $(\mathbf{x}_i)$ to predictions (i.e. labels).
Therefore, we can analyze $E_{DNN}$ absent of any training or test data. }

@@

The first two metrics are well-known in ML; the last two deserve special mention.
The empirical parameter $\alpha$ is the Power Law (PL) exponent that arises in the recently-developed HT-SR Theory~\cite{MM18_TR, MM19_HTSR_ICML, MM20_SDM}.
The bottom line from HT-SR Theory is that smaller values of $\alpha$ should correspond to models with better correlation over multiple size scales and thus to better models; see Appendix~\ref{sxn:theory-review-appendix} for more details.
Operationally, $\alpha$ is determined by analyzing DNN weight matrices using the publicly-available \emph{WeightWatcher} tool~\cite{weightwatcher_package} to fit the Empirical Spectral Density (ESD) of $\mathbf{X}$, i.e., a histogram of the eigenvalues, call it $\rho(\lambda)$, to a truncated PL, 
\begin{equation}
\rho(\lambda)\sim\lambda^{\alpha},\;\;\lambda\in[\lambda_{min},\lambda_{max}].
\end{equation}
Each of these quantities is defined for a given layer $\mathbf{W}$ matrix and the PL fitting method. \cite{Clauset}
\nred{Here, where $\lambda_{max}$ \emph{is} the largest eigenvalue of $\mathbf{X}=\mathbf{W}^{T}\mathbf{W}$, 
and $\lambda_{min}$ is selected automaticlly to yield the best PL fit (which minimizes the K-S distance). }

>>>>

Let us write the objective/optimization function (parameterized by $\mathbf{W}_{l}$s and $\mathbf{b}_{l}$s) for a DNN with $L$ layers, activation functions $h_{l}(\cdot)$, and $N\times M$ weight matrices $\mathbf{W}_{l}$ and biases $\mathbf{b}_{l}$, as 
the minimization of a general Loss Function $\mathcal{L}$ over $N$ training data instances and labels, $\{\mathbf{x}_{i},y_{i}\}\in\mathcal{D}$.
For a typical supervised classification problem, one has
\begin{equation}
\underset{\mathbf{W}_{l},\mathbf{b}_{L}}{\text{argmin}}\;\sum_{i=1}^{N}\left(\mathcal{L}(E_{DNN}(\mathbf{x}_{i})-y_{i})\right)  ,
\end{equation}
where the loss function $\mathcal{L}(\cdot)$ can take on a myriad of forms~\cite{JC17_TR}, and where
\begin{equation}
E_{DNN}=h_{L}(\mathbf{W}_{L}\times h_{L-1}(\mathbf{W}_{L-1}\times h_{L-2}(\cdots)+\mathbf{b}_{L-1})+\mathbf{b}_{L})
\label{eqn:dnn_energy}
\end{equation}
is what we call the Energy (or optimization) Landscape function.  
Notice that $E_{DNN}$ does not \emph{explicitly} depend on the data, but rather it maps data instance vectors (i.e., $\mathbf{x}_i$ values) to predictions (i.e., labels).
Therefore, we can analyze $E_{DNN}$ absent of any training or test data.

@@

The first two metrics are well-known in ML; the last two deserve special mention.
The empirical parameter $\alpha$ is the Power Law (PL) exponent that arises in the recently-developed HT-SR Theory~\cite{MM18_TR, MM19_HTSR_ICML, MM20_SDM}.
The bottom line from HT-SR Theory is that smaller values of $\alpha$ should correspond to models with better correlation over multiple size scales and thus to better models; see Appendix~\ref{sxn:theory-review-appendix} for more details.
Operationally, $\alpha$ is determined by analyzing DNN weight matrices using the publicly-available \emph{WeightWatcher} tool~\cite{weightwatcher_package} to fit the Empirical Spectral Density (ESD) of $\mathbf{X}$, i.e., a histogram of the eigenvalues, call it $\rho(\lambda)$, to a truncated PL, 
\begin{equation}
\rho(\lambda)\sim\lambda^{\alpha},\;\;\lambda\in[\lambda_{min},\lambda_{max}] ,
\end{equation}
where $\lambda_{max}$ is the largest eigenvalue of $\mathbf{X}=\mathbf{W}^{T}\mathbf{W}$, and 
where $\lambda_{min}$ is selected automatically to yield the best PL fit (which minimizes the K-S distance). 
Each of these quantities is defined for a given layer $\mathbf{W}$ matrix and the PL fitting method~\cite{CSN09_powerlaw,ABP14}.

### 2020-07-06 submission/nlp_models.tex
removed red and fixed some typos

The OpenAI GPT and GPT2 models provide us with the opportunity to analyze two effects: training the same model with different data set sizes; and increasing the sizes of both the data set and the architectures simultaneously.
These models have the remarkable ability to generate fake text that appears to the human to be real, and they have generated significant media attention because of the potential for their misuse.
For this reason, the original GPT model released by OpenAI was trained on a deficient data set, rendering the model interesting but not fully functional.  
Later, OpenAI released a much improved model, GPT2-small, which has the same architecture and number of layers as GPT, but which has been trained on a larger and better data set (and with other changes), making it remarkably good at generating (near) human-quality fake text.  
%
By comparing the poorly-trained (i.e., ``bad'') GPT to the well-trained (i.e., ``good'') GPT2-small, we can identify empirical indicators for when a model has in fact been poorly-trained and thus may perform poorly when deployed.
By comparing GPT2-medium to GPT2-large to GPT2-xl, we can examine the effect of increasing data set and model size simultaneously, as well as analyze well-trained versus more-well-trained models.

@@

This is important because it demonstrates that, while the Spectral (or Frobenius) norm may correlate well with predicted test error, at least among reasonably well-trained models, it is \emph{not} a good indicator of the overall model quality in general.
In particular, it can mispredict well-trained versus poorly-trained questions in ways not seen with PL-based metrics.
Using it as an empirical quality metric may give spurious results when applied to poorly-trained or otherwise deficient models.

@@

We now look across series of increasingly improving GPT2 models (i.e., we consider well-trained versus more-well-trained questions), by examining both the PL exponent $\alpha$ as well as the Log Norm metrics.  
In general, as we move from GPT2-medium to GPT2-xl, histograms for both $\alpha$ exponents and the Log Norm metrics downshift from larger to smaller values. 
For example, see Figure \ref{fig:gpt2-histograms}, which shows the histograms over the layer weight matrices for fitted PL exponent ($\alpha$) and the Log Alpha Norm ($\log\Vert\mathbf{W}\Vert_{\alpha}^{\alpha}$)~metric.

We see that the average $\alpha$ decreases with increasing model size, although the differences are less noticeable between the differing well-trained versus more-well-trained GTP2 models than between the poorly-trained versus well-trained GPT and GPT2-small models.
Unlike GPT, however, the layer Log Alpha Norms behave more as expected for GPT2 layers, with the larger models consistently having smaller norms. 
Similarly, the Log Spectral Norm also decreases on average with the larger models (not shown).  
As expected, the norm metrics can indeed distinguish among well-trained versus more-well-trained models among a series well-trained models.

We do notice, however, that while the peaks of the $\alpha$ are getting smaller, towards $2.0$, the tails of the distribution shifts right, with larger GPT2 models having more usually large $\alpha$ (also not shown).  
We suspect this indicates that these larger GPT2 models are still under-optimized/over-parameterized (relative to the data on which they were trained) and that they have capacity to support datasets even larger than the recent XL $1.5B$ release~\cite{gpt2-xl}.

>>>>

The OpenAI GPT and GPT2 models provide us with the opportunity to analyze two effects: training the same model with different data set sizes; and increasing the sizes of both the data set and the architectures simultaneously.
These models have the remarkable ability to generate fake text that appears to the human to be real, and they have generated significant media attention because of the potential for their misuse.
For this reason, the original GPT model released by OpenAI was trained on a deficient data set, rendering the model interesting but not fully functional.  
Later, OpenAI released a much improved model, GPT2-small, which has the same architecture and number of layers as GPT, but which has been trained on a larger and better data set (and with other changes), making it remarkably good at generating (near) human-quality fake text.  
%
By comparing the poorly-trained (i.e., ``bad'') GPT to the well-trained (i.e., ``good'') GPT2-small, we can identify empirical indicators for when a model has in fact been poorly-trained and thus may perform poorly when deployed.
By comparing GPT2-medium to GPT2-large to GPT2-xl, we can examine the effect of increasing data set and model size simultaneously, as well as analyze well-trained versus very-well-trained models.

@@

This is important because it demonstrates that, while the Spectral (or Frobenius) norm may correlate well with predicted test error, at least among reasonably well-trained models, it is \emph{not} a good indicator of the overall model quality in general.
In particular, it can mispredict well-trained versus poorly-trained questions in ways not seen with PL-based metrics.
Using it as an empirical quality metric may give spurious results when applied to poorly-trained or otherwise deficient~models.

@@

We now look across series of increasingly improving GPT2 models (i.e., we consider well-trained versus very-well-trained questions), by examining both the PL exponent $\alpha$ as well as the Log Norm metrics.  
In general, as we move from GPT2-medium to GPT2-xl, histograms for both $\alpha$ exponents and the Log Norm metrics downshift from larger to smaller values. 
For example, see Figure \ref{fig:gpt2-histograms}, which shows the histograms over the layer weight matrices for fitted PL exponent ($\alpha$) and the Log Alpha Norm ($\log\Vert\mathbf{W}\Vert_{\alpha}^{\alpha}$)~metric.

We see that the average $\alpha$ decreases with increasing model size, although the differences are less noticeable between the differing well-trained 
versus very-well-trained GTP2 models than between the poorly-trained versus well-trained GPT and GPT2-small models.
Unlike GPT, however, the layer Log Alpha Norms behave more as expected for GPT2 layers, with the larger models consistently having smaller norms. 
Similarly, the Log Spectral Norm also decreases on average with the larger models (not shown).  
As expected, the norm metrics can indeed distinguish among well-trained versus very-well-trained models among a series well-trained models.

We do notice, however, that while the peaks of the $\alpha$ are getting smaller, towards $2.0$, the tails of the distribution shifts right, with larger GPT2 models having more unusually large $\alpha$ (also not shown).  
We suspect this indicates that these larger GPT2 models are still under-optimized/over-parameterized (relative to the data on which they were trained) and that they have capacity to support datasets even larger than the recent XL $1.5B$ release~\cite{gpt2-xl}.
